### 2022-01-05 paper/paper.tex
adjust figures on p. 2
more details on Cartesian reference coordinates
reword parallelization feature
Co-authored-by: Michael Schlottke-Lakemper <michael@sloede.com>

Currently, \trixi provides shared-memory parallelization via multithreading.
Distributed-memory parallelization with MPI is available for some mesh types;
increasing the capability of this feature is subject to ongoing work.

@@

Figure~\ref{fig:jet} demonstrates sub-cell entropy-dissipative shock-capturing
methods with sub-cell positivity-preserving limiters and adaptive mesh refinement applied
to an astrophysical supersonic jet with Mach number 2000 \cite{liu2021oscillation}.
\begin{figure}[!h]
\vspace{-0.5em}
  \begin{subfigure}{0.53\linewidth}
    \includegraphics[width=\textwidth]{../figures/jet_density}
    \caption{Density at time $t = 10^{-3}$.}
  \end{subfigure}%
  \hspace*{\fill}
  \begin{subfigure}{0.47\linewidth}
    \includegraphics[width=\textwidth]{../figures/jet_mesh}
    \caption{Mesh at time $t = 10^{-3}$.}
  \end{subfigure}%
  \caption{Numerical solutions of a supersonic jet with Mach number 2000 using
           sub-cell entropy-dissipative shock-capturing methods with sub-cell positivity-preserving
           limiters and adaptive mesh refinement for the compressible Euler equations.}
  \label{fig:jet}
\end{figure}

@@

Figure~\ref{fig:pressure_waves} shows the approximation
of acoustic perturbation equations~\cite{ewert2003acoustic} wave scattering on a
curvilinear and unstructured domain. The 2D quadrilateral mesh used in the simulation
(Figure~\ref{fig:ginger_mesh}) was generated with
HOHQMesh.jl\xspace\footnote{\url{https://github.com/trixi-framework/HOHQMesh.jl}}.
\begin{figure}[!h]
  \begin{subfigure}{0.475\linewidth}
    \includegraphics[width=\textwidth]{../figures/ginger_time_00}
    \caption{Acoustic pressure at time $t = 0$.}
  \end{subfigure}%
  \hspace*{\fill}
  \begin{subfigure}{0.475\linewidth}
    \includegraphics[width=\textwidth]{../figures/ginger_time_08}
    \caption{Acoustic pressure at time $t = 8$.}
  \end{subfigure}%
  \\
  \begin{subfigure}{0.475\linewidth}
    \includegraphics[width=\textwidth]{../figures/ginger_time_16}
    \caption{Acoustic pressure at time $t = 16$.}
  \end{subfigure}%
  \hspace*{\fill}
  \begin{subfigure}{0.475\linewidth}
    \includegraphics[width=\textwidth]{../figures/ginger_mesh}
    \caption{Unstructured quad mesh.}
    \label{fig:ginger_mesh}
  \end{subfigure}%
  \caption{Numerical solutions of pressure wave scattering for the acoustic
                perturbation equations at three points in time as well as the unstructured,
                curvilinear quadrilateral mesh.}
  \label{fig:pressure_waves}
\end{figure}

@@

For the problem setup we consider a periodic box of the domain $[-1,1]^3$ with four elements in each
spatial direction. This results in $64 (\text{\lstinline{polydeg}}+1)^3$ degrees
of freedom (DG nodes) per equation when polynomials of degree \lstinline{polydeg} are used.
To make the mesh curvilinear, the interior of the box is heavily warped by
a mapping adapted from \cite{chan2019efficient}.
Specifically, we map Cartesian reference coordinates $(\xi, \eta, \zeta)$ to
physical coordinates $(x, y, z)$ via the transformation
\begin{equation}
\begin{aligned}
  y &= \eta  + 0.15 \bigl( \cos(1.5 \pi \xi) \cos(0.5 \pi \eta) \cos(0.5 \pi \zeta) \bigr),
  \\
  x &= \xi   + 0.15 \bigl( \cos(0.5 \pi \xi) \cos(2 \pi y) \cos(0.5 \pi \zeta) \bigr),
  \\
  z &= \zeta + 0.15 \bigl( \cos(0.5 \pi x) \cos(\pi y) \cos(0.5 \pi \zeta) \bigr).
\end{aligned}
\end{equation}
To integrate up to the
final time $T=1.0$, both codes use the five-stage, fourth-order low-storage explicit
Runge-Kutta method of Carpenter and Kennedy~\cite{CarpenterKennedy1994}.
A stable explicit time step is adaptively computed according to the local maximum wave
speed, the relative grid size, and an adjustable Courant-Friedrichs-Lewy (CFL)
coefficient $\text{CFL}\in(0,1]$~\cite{gassner2011}. For the performance computations presented herein
we fix this coefficient to be $\text{CFL}=0.5$.

>>>>

Currently, \trixi provides shared-memory parallelization via multithreading.
Initial parallelization with MPI is available for some mesh types,
but full support for distributed-memory parallelism is subject to ongoing work.

@@

Figure~\ref{fig:jet} demonstrates sub-cell entropy-dissipative shock-capturing
methods with sub-cell positivity-preserving limiters and adaptive mesh refinement applied
to an astrophysical supersonic jet with Mach number 2000 \cite{liu2021oscillation}.
\begin{figure}[!h]
\vspace{-0.5em}
  \begin{subfigure}{0.53\linewidth}
    \includegraphics[width=\textwidth]{../figures/jet_density}
    \caption{Density at time $t = 10^{-3}$.}
  \end{subfigure}%
  \hspace*{\fill}
  \begin{subfigure}{0.47\linewidth}
    \includegraphics[width=\textwidth]{../figures/jet_mesh}
    \caption{Mesh at time $t = 10^{-3}$.}
  \end{subfigure}%
  \caption{Numerical solutions of a supersonic jet with Mach number 2000 using
           sub-cell entropy-dissipative shock-capturing methods with sub-cell positivity-preserving
           limiters and adaptive mesh refinement for the compressible Euler equations.}
  \label{fig:jet}
\vspace{-0.5em}
\end{figure}

@@

Figure~\ref{fig:pressure_waves} shows the approximation
of acoustic perturbation equations~\cite{ewert2003acoustic} wave scattering on a
curvilinear and unstructured domain. The 2D quadrilateral mesh used in the simulation
(Figure~\ref{fig:ginger_mesh}) was generated with
HOHQMesh.jl\xspace\footnote{\url{https://github.com/trixi-framework/HOHQMesh.jl}}.
\begin{figure}[!h]
\vspace{-0.5em}
  \begin{subfigure}{0.475\linewidth}
    \includegraphics[width=\textwidth]{../figures/ginger_time_00}
    \caption{Acoustic pressure at time $t = 0$.}
  \end{subfigure}%
  \hspace*{\fill}
  \begin{subfigure}{0.475\linewidth}
    \includegraphics[width=\textwidth]{../figures/ginger_time_08}
    \caption{Acoustic pressure at time $t = 8$.}
  \end{subfigure}%
  \\
  \begin{subfigure}{0.475\linewidth}
    \includegraphics[width=\textwidth]{../figures/ginger_time_16}
    \caption{Acoustic pressure at time $t = 16$.}
  \end{subfigure}%
  \hspace*{\fill}
  \begin{subfigure}{0.475\linewidth}
    \includegraphics[width=\textwidth]{../figures/ginger_mesh}
    \caption{Unstructured quad mesh.}
    \label{fig:ginger_mesh}
  \end{subfigure}%
  \caption{Numerical solutions of pressure wave scattering for the acoustic
                perturbation equations at three points in time as well as the unstructured,
                curvilinear quadrilateral mesh.}
  \label{fig:pressure_waves}
\end{figure}

@@

For the problem setup we consider a periodic box of the domain $[-1,1]^3$ with four elements in each
spatial direction. This results in $64 (\text{\lstinline{polydeg}}+1)^3$ degrees
of freedom (DG nodes) per equation when polynomials of degree \lstinline{polydeg} are used.
To make the mesh curvilinear, the interior of the box is heavily warped by
a mapping adapted from \cite{chan2019efficient}.
Specifically, we map Cartesian reference coordinates $(\xi, \eta, \zeta) \in [-1, 1]^3$
to physical coordinates $(x, y, z)$ via the transformation
\begin{equation}
\begin{aligned}
  y &= \eta  + 0.15 \bigl( \cos(1.5 \pi \xi) \cos(0.5 \pi \eta) \cos(0.5 \pi \zeta) \bigr),
  \\
  x &= \xi   + 0.15 \bigl( \cos(0.5 \pi \xi) \cos(2 \pi y) \cos(0.5 \pi \zeta) \bigr),
  \\
  z &= \zeta + 0.15 \bigl( \cos(0.5 \pi x) \cos(\pi y) \cos(0.5 \pi \zeta) \bigr).
\end{aligned}
\end{equation}
To integrate up to the
final time $T=1.0$, both codes use the five-stage, fourth-order low-storage explicit
Runge-Kutta method of Carpenter and Kennedy~\cite{CarpenterKennedy1994}.
A stable explicit time step is adaptively computed according to the local maximum wave
speed, the relative grid size, and an adjustable Courant-Friedrichs-Lewy (CFL)
coefficient $\text{CFL}\in(0,1]$~\cite{gassner2011}. For the performance computations presented herein
we fix this coefficient to be $\text{CFL}=0.5$.
